% !TEX program = xelatex
\documentclass{mycv}
\usepackage{tabularx}
\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{changepage}

% \newcommand\CC{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\relsize{-2}{\textbf{++}}}}
% \newcommand\CC{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{++}}
\newcommand\CC{C\texttt{++}}

\begin{document}

%------------------------------------------------------------------------------
% Header
%------------------------------------------------------------------------------
\name{Selim Belhaouane}
% \subtitle{Software Engineer}
\setphone{+1 (514) 891-9225}
\setemail{selim.belhaouane@gmail.com}
\setgithub{selimb}
\setlinkedin{selimbelhaouane}
\header{\phone}{\github}{\email}{\linkedin}

\begin{objective}
    Resourceful software engineer with 10+ years building diverse software systems, including web applications, computer vision for IoT, developer tools, and CAD/CAE automation.
    Known for solving complex challenges and diving deep into topics, with a proven track record as a self-taught tech lead.
    Passionate about distributed systems, automation, and databases.
    Eager to learn from others and equally enthusiastic about sharing knowledge.
\end{objective}

\vspace{-\parskip}\noindent\rule{\textwidth}{0.4pt}

\section{experience}

\begin{sectionindent}
    %
    % GardaWorld Security
    %
    \entryhead{GardaWorld and ECAMSECURE}{Montreal, Canada}
    \position{Team Lead}{2022 — Now}

    Started and lead development of a remote video monitoring solution leveraging AI technology at the edge and in the cloud.

    \begin{itemize}
        \item Generated millions in revenue within a few years.
        \item Led the design and implementation of a full-stack web application.
        \item Contributed to the development of a mobile application using React Native.
        \item Designed and implemented a fault-tolerant and scalable architecture, with message buses and several layers of caching, to handle over 2 million daily video events.
        \item Routinely performed PostgreSQL performance tuning, including data modeling, query optimization, EXPLAIN plan analysis and index refinement.
        \item Enabled distributed tracing and alerts in Datadog to improve observability and debugging.
        \item Managed and mentored a team of five, driving successful delivery of a complex system under tight resource constraints.
    \end{itemize}

    \tagline{Python, OpenCV, Pytorch, Typescript, React, React Native, Next.js, REST, Rust, PostgreSQL, Redis, Azure, Docker, Datadog}

    \vspace{2\parskip}

    %
    % Maya
    %
    \entryhead{MAYA Heat Transfer Technologies Ltd.}{Montreal, Canada}
    \position{Team Lead}{2020 — 2022}

    Started and led full-stack development of \href{https://blogs.sw.siemens.com/simcenter/simcenter-3d-2022-1-remote-solve/}{\itfont{Remote Simulation}}, a distributed HPC platform integrated with Siemens Simcenter 3D, a leading CAD/CAE product.

    \begin{itemize}
        \item Architected and developed the entire system, including web application, Simcenter 3D GUI plugin, and distributed job runners.
        \item Enabled real-time solution monitoring and interactive 3D visualizations for improved simulation workflows.
        % \item Delivered a seamless integration with Simcenter 3D, enhancing user experience and productivity in high-performance simulation environments.
        \item Led a team of four engineers, fostering collaboration and growth.
    \end{itemize}

    \tagline{Python, Django, FastAPI, React, Typescript, Cypress, Nginx, PostgreSQL, Docker, \CC, Qt}

    \position{Technical Lead}{2017 — 2020}

    Led development of Siemens Simcenter 3D plugins to enhance functionality and improve productivity for mechanical engineering (CAD/CAE) workflows.

    \begin{itemize}
        \item Led software development guild meetings after just a year as a professional SWE.
        % \item Stood out among team members by leveraging strong mathematical background to grasp complex customer requirements.
        % \item Developed a Python library and tools for rapid application prototyping, empowering mechanical engineers to streamline their workflows; authored extensive documentation and training materials to support adoption.
        \item Onboarded, code-reviewed, and provided guidance to junior developers, fostering growth and maintaining high-quality code standards.
    \end{itemize}

    \tagline{Python, \CC, .NET Framework}

    % \vspace{\parskip}
    %
    % McGill (IRRELEVANT)
    %
    % \entryhead{McGill Centre for Intelligent Machines}{Montreal, Canada}
    % \position{Undergraduate Researcher}{\small{Summer} 2013}

    % Realistic modeling of friction forces at contact between rigid bodies.

    % \tagline{MATLAB}

\end{sectionindent}

\section{education}

\begin{sectionindent}
    %
    % Master's
    %
    \entryhead{M.Eng Thesis}{McGill University}
    \position{Mechanical Engineering}{2015 — 2017}
    Master's in computational fluid dynamics, sponsored by Maya Heat Transfer Technologies.
    \begin{itemize}
        \item Thesis on implementation and validation of turbulence model in academic and commercial (NX Flow) finite volume codes.
        \item Used NX Open, Tecplot and Python for pre-processing and/or post-processing purposes.
        \item Developed web interface for querying the in-house test suite, now an essential part of the development process.
    \end{itemize}

    \tagline{Python, Matplotlib, Tecplot, \CC, Fortran, MPI, jQuery, \LaTeX{}}

    \vspace{2\parskip}

    %
    % Bachelor's
    %
    \entryhead{B.Eng}{McGill University}
    \position{Mechanical Engineering}{2011 — 2015}
    \begin{itemize}
        \item Designed and manufactured carbon fiber steering wheel as part of Capstone project with McGill Racing Team.
        \item Gave extracurricular classes on \LaTeX{}.
    \end{itemize}

    \tagline{Python, MATLAB, C, Fortran, \LaTeX{}}
\end{sectionindent}

% \section{certifications}

% \begin{sectionindent}
%     \entryhead{Agile Foundation Training}{\itfont October 2019}
% \end{sectionindent}

\end{document}